%-------------------------
% Resume in Latex
% Author : Victory Omole
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
 \textbf {Victory Omole} & Email : vtomole@iastate.edu\\
  https://github.com/vtomole & Phone : 515-259-7269 \\
\end{tabular*}
\section{Objective}
Seeking an intership or co-op that will allow me to take full advantage of my passion
and experience in Software Engineering.
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Iowa State University}{Ames, IA}
      {Bachelor of Science, Computer Engineering}{Expected graduation: May 2018}
  \resumeSubHeadingListEnd
  \section{Honor}
  Iowa State Dean’s List, Spring 2017.
  %-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

      \resumeSubheading
      {qc-hack-harvard}{https://github.com/vtomole/qc-hack-harvard}
      {Visualizing quantum computing algorithms in the browser}{October 2017 - Present}
      \resumeItemListStart
        \resumeItem{Virtual machine}
                   {Implemented a virtual machine in Python to execute Quantum Algorithms for the frontend.}
                   \resumeItem{Hack Harvard}
          {Won the Hacker Prize (Sharing information openly; doing something for its own sake; finding creative solutions to problems.) at Hack Harvard.}
          \resumeItemListEnd
    \resumeSubheading
      {C48}{https://github.com/vtomole/c48}
      {A Modern Scalable Programming Language}{September 2017 - Present}
      \resumeItemListStart
        \resumeItem{Parser}
          {Implemented a parser that can parse arithmetic expressions and build an abstract syntax tree out of these expressions.}
        \resumeItem{Intepreter}
          {Implemented an intepreter that can walk the absract syntax tree and apply function operators to it's arguments.}
          \resumeItemListEnd

       
           \resumeSubheading
      {Evie}{https://github.com/vtomole/evie}
      {A Programming Language Playground}{September 2016 - Present}
      \resumeItemListStart
        \resumeItem{Cantor}
          {Wrote a programming language inspired by Set Theory that won a prize for ``Most interesting project'' in a Fall 2016 Hackathon.}
        \resumeItem{Shell}
                   {Implemented a Shell intepreter that is capable of executing Linux shell commands.}

                    \resumeItem{Kiana}
                               {Wrote a virtual machine that is capable of interpreting an assembly language.}
                             
          \resumeItemListEnd


           \resumeSubheading
           {Victorys AI Playground}{https://github.com/vtomole/victorysaiplayground}
      {Documenting my education on Machine Learning}{May 2016 - August 2016}
      \resumeItemListStart
        \resumeItem{AIPlayground}
          {Programmed basic neural networks in Jupyter Notebook, then trained these neural networks on a GPU.}
        \resumeItem{Blog}
          {Implemented in Django and deployed using Heroku: https://victorysaiplayground.herokuapp.com/ }
      \resumeItemListEnd

   

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\textbf{Skilled}: Java, C,  Quantum Computing, Common Lisp, Scheme

\textbf{Experienced}: Python, Linux, Git, BASH, Emacs, HTML

\textbf{Basic competancy}: Javascript, PHP, C++, Ruby


%-------------------------------------------

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Iowa State Academic Success Center}{Ames, IA}
      {Tutor}{September 2017 - Present}
      \resumeItemListStart
        \resumeItem{Tasks}
          {I help students understand the material that is taught in the ``Theoretical Foundations in Computer Engineering'' class. I am also tutoring a ``MultiVariable Calculus'' class. }
      \resumeItemListEnd

    %\resumeSubheading
     % {Home Depot}{Plymouth, MN}
      %{Freight Team}{Summer of 2015 and 2016}
      %\resumeItemListStart
       %\resumeItem{Tasks}{Stocked shelves and hepled customers find items.}
              
     % \resumeItemListEnd

   

  \resumeSubHeadingListEnd

  \section{Writing}
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Architecture for a trapped ion quantum computer} & https://vtomole.github.io/static/microwave-arch.pdf\\
\end{tabular*}
  
  
\end{document}
